\ttitle

### 2015-08-22 Tables/c1_clavien_dindo.tex
Introduction - revision to section 1.3
- Spelling, grammar, style corrections
Review 1 - Introduction
- Fixed nearly all incomplete sections
- All todos sorted
- Multiple tables amended for formatting
- More references for jaundice, immunity
- Added table for POSSUM
- Fixed several overfull box issues with TOC

\begin{sidewaystable}[htbp]
\caption{The Clavien-Dindo Classification of Surgical Complications}
\label{table:clavien-dindo}
\centering
\begin{tabular}{|l m{15cm}|}
 \hline
 Grade  &   Description  \\ \hline

 Grade I     &   Any deviation from the normal postoperative course without the need for pharmacological treatment or surgical, endoscopic and radiological interventions. \\

Grade II      &   Requiring pharmacological treatment with drugs other than such allowed for grade I complications. Blood transfusions and total parenteral nutrition are also included.\\ 
Grade III     &   Requiring surgical, endoscopic or radiological intervention\\
                &  Grade III-a: - intervention not under general anesthesia\\
                &  Grade III-b: - intervention under general anesthesia\\ 
Grade IV       &  Life-threatening complication (including CNS complications)‡ requiring IC/ICU-management\\
                &   Grade IV-a: - single organ dysfunction (including dialysis)\\
                &   Grade IV-b: - multi organ dysfunction\\ 
Grade V        &   Death of a patient\\ \hline
Suffix 'd':     &   If the patients suffers from a complication at the time of discharge,  the suffix  “d”  (for ‘disability’) is added to the respective grade of complication. This label indicates the need for a follow-up to fully evaluate the complication.\\ \hline

\end{tabular}

\end{sidewaystable}

>>>>

\begin{sidewaystable}[htbp]
	\centering
	\caption{The Clavien-Dindo classification of surgical complications.}
	\label{table:clavien-dindo}	
	\renewcommand{\arraystretch}{1.7} %Increases space between rows
	\setlength{\tabcolsep}{14pt} %sets the space between columns
	\begin{tabular}{|l m{15cm}|}
		\hline
		Grade       & Description \\ \hline
		Grade I     & Any deviation from the normal postoperative course without the need for pharmacological treatment or surgical, endoscopic and radiological interventions.  \\
		Grade II    & Requiring pharmacological treatment with drugs other than such allowed for grade I complications. Blood transfusions and total parenteral nutrition are also included.  \\
		Grade III   & Requiring surgical, endoscopic or radiological intervention  \\
		            & Grade III-a: - intervention not under general anaesthesia \\
		            & Grade III-b: - intervention under general anaesthesia  \\
		Grade IV    & Life-threatening complication (including CNS complications)‡ requiring  HDU/ICU-management  \\
		            & Grade IV-a: - single organ dysfunction (including dialysis)     \\
		            & Grade IV-b: - multi organ dysfunction \\
		Grade V     & Death of a patient  \\ \hline
		Suffix 'd': & If the patients suffers from a complication at the time of discharge,  the suffix  “d”  (for ‘disability’) is added to the respective grade of complication. This label indicates the need for a follow-up to fully evaluate the complication. \\ \hline
	\end{tabular}
\end{sidewaystable}

### 2015-08-22 Tables/c1_cpet_parameters.tex
Review 1 - Introduction
- Fixed nearly all incomplete sections
- All todos sorted
- Multiple tables amended for formatting
- More references for jaundice, immunity
- Added table for POSSUM
- Fixed several overfull box issues with TOC

\begin{table}[p]
\centering
\caption{Parameters measured at spirometry.}
\label{table:spirometry}
\begin{tabular}{| m{2cm}  m{2cm}  m{7cm} |}
	\hline
	Parameter & Units  & Description                          \\ \hline
	FVC       & litres & Forced Vital Capacity                \\
	FEV1      & litres & Forced Expiratory Volume in 1 second \\
	FEV1/FVC  & \%     & Tiffeneau-Pinelli[1] index           \\ \hline
\end{tabular}

@@

\caption{Common parameters measured at cardiopulmonary exercise testing.}
\label{table:cpet_parameters}
\begin{tabular}{| m{2cm}  m{2cm}  m{7cm} |}
	\hline
	Parameter & Units       & Description                                  \\ \hline
	\%peakVO2 & \%          & VO2 as a \% of predicted VO2Peak             \\
	Load      & Watts       & Exercise Workload                            \\
	VE        & litres/min  & Ventilatory Equivalent                       \\
	Vt        & litres      & Tidal volume                                 \\
	VO2       & litres/min  & Absolute Oxygen uptake/consumption           \\
	VO2/kg    & ml/(kg*min) & Corrected Oxygen uptake/consumption          \\
	VE/VO2    &             & Ventilatory Equivalent for O$_2$             \\
	VCO2      & litres/min  & Carbon-dioxide output                        \\
	VE/VCO2   &             & Ventilatory Equivalent for CO$_2$            \\
	RER       &             & Respiratory Exchange Ratio                   \\
	PETO2     & mmHg        & End Tidal O2                                 \\
	PETCO2    & mmHg        & End Tidal CO2                                \\
	O2Pulse   & ml/beat     & Oxygen pulse                                 \\
	HR        & beats/min   & Heart Rate                                   \\
	Bf        & /min        & Breathing Frequency                          \\
	P(A-a)O2  & mmHg        & Alveolar-arterial PO2 difference             \\
	Vd/Vt     &             & Physiologic dead space-to-tidal volume ratio \\
	SBP       & mmHg        & Systolic blood pressure                      \\
	DBP       & mmHg        & Diastolic blood pressure                     \\
	O2sat     & \%          & Oxygen saturation                            \\ \hline
\end{tabular}

>>>>

\begin{table}[p]
	\centering
	\caption{Parameters measured at spirometry.}
	\label{table:spirometry}
	\renewcommand{\arraystretch}{1.5} %Increases space between rows
	\setlength{\tabcolsep}{10pt} %sets the space between columns
	\begin{tabular}{| m{2cm}  m{2cm}  m{7.7cm} |}
		\hline
		Parameter & Units  & Description                          \\ \hline
		FVC       & litres & Forced Vital Capacity                \\
		FEV1      & litres & Forced Expiratory Volume in 1 second \\
		FEV1/FVC  & \%     & Tiffeneau-Pinelli index              \\ \hline
	\end{tabular}

@@

	\caption{Common parameters measured at cardiopulmonary exercise testing.}
	\label{table:cpet_parameters}
	\begin{tabular}{| m{2cm}  m{2cm}  m{7.7cm} |}
		\hline
		Parameter                  & Units      & Description                         \\ \hline
		Load                       & Watts      & Exercise Workload                   \\
		$\dot{V}_E$                & litres/min & Ventilatory Equivalent              \\
		Vt                         & litres     & Tidal volume                        \\
		$\dot{V}_{O_2}$            & litres/min & Absolute Oxygen uptake/consumption  \\
		$\dot{V}_{O_2}$/kg         & ml//kg/min & Corrected Oxygen uptake/consumption \\
		$\dot{V}_E/\dot{V}_{O_2}$  &            & Ventilatory Equivalent for $O_2$    \\
		$\dot{V}_{CO_2}$           & litres/min & Carbon-dioxide output               \\
		$\dot{V}_E/\dot{V}_{CO_2}$ &            & Ventilatory Equivalent for $CO_2$   \\
		RER                        &            & Respiratory Exchange Ratio          \\
		$PET_{O_2}$                & mmHg       & End Tidal $O_2$                     \\
		$PET_{CO_2}$               & mmHg       & End Tidal $CO_2$                    \\
		${O_2}$Pulse               & ml/beat    & Oxygen pulse                        \\
		HR                         & beats/min  & Heart Rate                          \\
		$B_f$                      & resps/min  & Breathing Frequency                 \\ \hline
	\end{tabular}

### 2015-08-22 Tables/c1_isgps.tex
Minor changes to Introduction
- Include section labels for POPF, PPH
- vfill/hfill in ISGPS tables
Review 1 - Introduction
- Fixed nearly all incomplete sections
- All todos sorted
- Multiple tables amended for formatting
- More references for jaundice, immunity
- Added table for POSSUM
- Fixed several overfull box issues with TOC

\begin{sidewaystable}[htbp]
\centering
\caption{Postoperative pancreatic fistula: ISGPF definition.}
\label{table:isgps_popf}
\begin{tabular}{|m{4cm}|m{4cm}|m{5cm}|m{5cm}|}
	\hline
	Grade                                & A        & B                 & C                 \\ \hline
	Clinical conditions                  & Well     & Often well        & Ill appearing/bad \\
	Specific treatment                   & No       & Yes/no            & Yes               \\
	US/CT (if obtained)                  & Negative & Negative/positive & Positive          \\
	Persistent drainage (after 3 weeks)† & No       & Usually yes       & Yes               \\
	Reoperation                          & No       & No                & Yes               \\
	Death related to POPF                & No       & No                & Possibly yes      \\
	Signs of infections                  & No       & Yes               & Yes               \\
	Sepsis                               & No       & No                & Yes               \\
	Readmission                          & No       & Yes/no            & Yes/no            \\ \hline
\end{tabular}

\caption{Postpancreatectomy haemorrhage: ISGPS definition.}
\label{table:isgps_pph}
\begin{tabular}{|m{4cm}|m{4cm}|m{5cm}|m{5cm}|}
	\hline
	Grade                                                             & A                                                                                & B                                                                                                                             & C                                                                                         \\ \hline
	Time of onset, location, severity and clinical impact of bleeding & Early, intra- or extraluminal, mild                                              & Early, intra- or extraluminal, severe	or Late, intra- or extraluminal, mild                                                   & Late, intra- or extraluminal, severe                                                      \\
	Clinical condition                                                & Well                                                                             & Often well/ intermediate, very rarely life-threatening                                                                        & Severely impaired, life-threatening                                                       \\
	Diagnostic consequence                                            & Observation, blood count, ultrasonography and, if necessary, computed tomography & Observation, blood count, ultrasonography, computed tomography, angiography, endoscopy                                        & Angiography, computed tomography, endoscopy                                               \\
	Therapeutic consequence                                           & No                                                                               & Transfusion of fluid/blood, intermediate care unit (or ICU), therapeutic endoscopy,† embolization, relaparotomy for early PPH & Localization of bleeding, angiography and embolization, (endoscopy†) or relaparotomy, ICU \\ \hline
\end{tabular}
\end{sidewaystable}

>>>>

\begin{sidewaystable}[htbp]
\centering
\footnotesize
\caption{Postoperative pancreatic fistula: ISGPF definition.}
\label{table:isgps_popf}
\renewcommand{\arraystretch}{1.2} %Increases space between rows
%\setlength{\tabcolsep}{10pt} %sets the space between columns
\begin{tabular}{|p{4.5cm}|p{4cm}|p{5cm}|p{5cm}|}
	\hline
	Grade                                & A        & B                 & C                                                   \\ \hline
	Clinical conditions                  & Well     & Often well        & Ill appearing/bad                                   \\
	Specific treatment                   & No       & Yes/no            & Yes                                                 \\
	US/CT (if obtained)                  & Negative & Negative/positive & Positive                                            \\
	Persistent drainage (after 3 weeks)† & No       & Usually yes       & Yes                                                 \\
	Reoperation                          & No       & No                & Yes                                                 \\
	Death related to POPF                & No       & No                & Possibly yes                                        \\
	Signs of infections                  & No       & Yes               & Yes                                                 \\
	Sepsis                               & No       & No                & Yes                                                 \\
	Readmission                          & No       & Yes/no            & Yes/no                                              \\ \hline
\end{tabular}

\vspace{0.7cm}

\caption{Postpancreatectomy haemorrhage: ISGPS definition.}
\label{table:isgps_pph}
\begin{tabular}{|m{4.5cm}|m{4cm}|m{5cm}|m{5cm}|}
	\hline
	Grade                                                             & A                                                                                & B                                                                                                                             & C                                                                                         \\ \hline
	Time of onset, location, severity and clinical impact of bleeding & Early, intra- or extraluminal, mild                                              & Early, intra- or extraluminal, severe	or Late, intra- or extraluminal, mild                                                   & Late, intra- or extraluminal, severe                                                      \\
	Clinical condition                                                & Well                                                                             & Often well/ intermediate, very rarely life-threatening                                                                        & Life-threatening, severely impaired                                                      \\
	Diagnostic consequence                                            & Observation, blood count, ultrasonography and, if necessary, computed tomography & Observation, blood count, ultrasonography, endoscopy, computed tomography, angiography                                      & Angiography, endoscopy, computed tomography                                              \\
	Therapeutic consequence                                           & No                                                                               & Transfusion of fluid/blood, intermediate care unit (or ICU), therapeutic endoscopy,† embolization, relaparotomy for early PPH & Localization of bleeding, angiography and embolization, (endoscopy†) or relaparotomy, ICU \\ \hline
\end{tabular}
\end{sidewaystable}
